Exploring the Role of Small Molecules in Biological Systems Using Network Approaches

### 2014-12-30 paper.tex
Started section on scaffold networks Added discussion points

@@

\section{Summary}
\label{sec:summary}

\bibliography{paper}

>>>>

The notion of a scaffold is common place in medicinal chemistry and is
usually considered to be a ring-containing substructure pruned of
sidechains that represents the core structure of a series of
molecules. An example is the tricyclic core common to a number of
antidepressants (e.g., amitriptylene and imipramine) shown in Figure
\ref{fig:tca-core}. Scaffolds allow one to summarize a collection of
molecules (such as in patent claims) and one can usually assume that
compounds with the same scaffold will share a common synthetic pathway
or even a common mechanism of action.

While a number of approaches have been described to generate scaffolds
\cite{Lewell:1998aa,Bemis:1996aa,Katritzky:2000wf}, a few approaches
have considered hierarchical decomposition of scaffolds. Examples
include the HierS method \cite{Wilkens:2005il} and the Scaffold Tree
method \cite{Schuffenhauer:2007oz}.

\ctable[cap={}, caption={An example of a scaffold. In this case, this
  scaffold is common to many tricyclic antidepressants}, figure, botcap,
label={fig:tca-core}]    
{c}
{}
{\includegraphics{img/tca-core}}

@@

\section{Discussion}
\label{sec:summary}

\begin{itemize}
\item Networks on the chemistry side tend to be more for visualization
\item In many cases the network does not necessarily lead to nove output
\item A key utility of network approaches is the ability to integrate
  different data types such as small molecules and proteins
\item Networks represent an approach to representing multiple
  relationships in a single contruct - multiple properties of a
  relatinship between two entities can be encoded by edge properties
  (width, color, length). Similarly multiple properties of a given
  entity can be encoded in node properties (size, shape, color) 
\end{itemize}
\bibliography{paper}
